\RequirePackage{filecontents}
\begin{filecontents*}{moderncvcolorindigo.sty}
%% start of file `moderncvcolorburgundy.sty'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

%-------------------------------------------------------------------------------
%                identification
%-------------------------------------------------------------------------------
\NeedsTeXFormat{LaTeX2e}
\ProvidesPackage{moderncvcolorindigo}[2013/02/09 v1.3.0 modern curriculum vitae and letter color scheme: burgundy]

%-------------------------------------------------------------------------------
%                color scheme definition
%-------------------------------------------------------------------------------
\definecolor{color0}{rgb}{0,0,0} % black
\definecolor{color1}{HTML}{3F51B5} % indigo_500 from color palette provided in material design guidelines
\definecolor{color2}{rgb}{0.45,0.45,0.45} % dark grey
\endinput
%% end of file `moderncvcolorburgundy.sty'.
\end{filecontents*}

\begin{filecontents}{bibliography_en.bib}
@article{skobtsov08a,
	Author = {Skobtsov, Y. A. and Balabanov, V. N.},
	Journal = {Herald of Khmelnytskyi national university; Series: ``Technical sciences''},
	Number = {4},
	Pages = {205--217},
	Title = {A review of the application of meta\-/heuristic algorithms to the cutting stock and packing problems},
	Volume = {1},
	Year = {2008}}

@article{balabanov09a,
	Author = {Balabanov, V. N. and Skobtsov, Y. A. and Fonotov, A. M.},
	Journal = {Scientific Papers of Donetsk National Technical University; Series: ``Computers and automation''},
	Number = {148},
	Pages = {119--126},
	Title = {Dataware issues in cutting stock and packing problems},
	Volume = {17},
	Year = {2009}}

@article{balabanov09b,
	Author = {Balabanov, V. N.},
	Journal = {The problems of information technologies},
	Number = {2},
	Title = {Solving roll trim problem with multiple objectives},
	Volume = {6},
	Year = {2009}}

@article{balabanov10a,
	Author = {Balabanov, V. N. and Skobtsov, Y. A.},
	Journal = {Herald of the DSEA},
	Number = {1},
	Pages = {7--12},
	Title = {Trim-loss optimization for coil slitting problem},
	Volume = {18},
	Year = {2010}}

@article{balabanov10b,
	Author = {Balabanov, V. N.},
	Journal = {Herald of the National Technical University ``KhPI''; Subject issue: ``Information Science and Modelling''},
	Number = {31},
	Pages = {4--9},
	Title = {Evolutionary approach for roll trim planning in production of electric\-/welded pipes},
	Volume = {15},
	Year = {2010}}

@article{balabanov14,
	Author = {Balabanov, V. N. and Skobtsov, Y. A.},
	Journal = {Izvestiya SFedU. Engineering sciences},
	Month = {1},
	Number = {150},
	Pages = {44--55},
	Title = {An evolutionary algorithm for optimization of roll cutting},
	Year = {2014}}
\end{filecontents}


\documentclass[11pt,a4paper,roman]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.82]{geometry}
\usepackage[shortcuts]{extdash}
\usepackage{etoolbox}
\usepackage[autostyle]{csquotes}
\usepackage[symbol,norule,hang,flushmargin]{footmisc}

\usepackage[unicode]{hyperref}
\definecolor{linkcolor}{HTML}{303F9F} % indigo_700 from color palette provided in material design guidelines
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolor, linkcolor=linkcolor}

\moderncvstyle{classic}
\moderncvcolor{indigo}

\makeatletter
\renewcommand*{\quotefont}{\normalfont}
\renewcommand*{\quotestyle}[1]{{\quotefont\textcolor{color2}{#1}}}
\makeatother

\makeatletter
\renewcommand\@makefnmark{\hbox{\@textsuperscript{\normalfont\color{color2}\@thefnmark}}}
\makeatother

\renewcommand*{\mobilephonesymbol}{\fixedphonesymbol}
\apptocmd
    {\bibliographyhead}
    {\cvline
        {}
        {\textit{All publications are available only in Russian.}\smallskip}
    }
    {}{}
    
\providetoggle{is_nda_compliant}
\settoggle{is_nda_compliant}{false}

% personal data
\name{Victor}{Balabanov}
\title{Android developer}
\address{Kyiv, Ukraine}
\phone[mobile]{+38~(091)~924~2116}
\email{akavrt@gmail.com}
\social[github]{akavrt}
\quote{\enquote{Life is too short to run boring applications}}

\begin{document}

\makecvtitle

\section{Brief description}
\cvline
    {}
    {I'm experienced Android developer with strong Java background. My primary 
    interest lies in development of responsive user-centric mobile applications 
    with pixel-perfect user interface and carefully built tech underwear.}


\medskip
\section{Technical skills}
\cvitem
    {Languages}
    {Java, C}
\cvitem
    {Frameworks}
    {Core Android application framework components (with SDK platforms 
    corresponding to Android versions from 2.3 and above), location and 
	sensor APIs, MediaPlayer, ExoPlayer, Google Cast Android SDK, 
	Android TV with Leanback Support Library templates, 
	SQLite (including SpatiaLite and SQLCipher extensions).}
\cvitem
    {Libraries}
    {Android Support Library package, Google Play Services, suite of libraries 
    maintained by Square including OkHttp, Retrofit, Picasso and Otto.}
\cvitem
    {Testing}
    {JUnit, Espresso.}
\cvitem
    {Tools}
    {Android Studio, Eclipse with ADT plugin, Gradle, Maven, Jenkins CI, 
    Fabric.}
\cvitem
    {VCS}
    {Git, Mercurial.}
\cvitem
    {Productivity}
    {JIRA, Redmine, Trello.}
    

\medskip
\section{Work experience}

\cventry
    {June 2014 --\\Present}
    {Senior Android developer}
    {\href{http://x2sy.com/}{X2SY}}
    {Kyiv}{Ukraine}
    {
        \iftoggle{is_nda_compliant}
            {
                Building Android app with advanced media playback features for
                an industry-leading local OTT service.\newline
            }
            {
                Building a set of mobile and TV user-friendly Android apps with 
				advanced media playback features for 
				\href{http://megogo.net/}{MEGOGO.NET}~--- an industry-leading 
                local OTT service.
                Working on the proprietary VAST-compliant video player which 
				supports content protected with Widevine Classic DRM, HLS and  
				MPEG-DASH adaptive playbacks, as well as  different types of 
				video ads.
				The core playback features are implemented by using Google's 
				modern ExoPlayer library, more traditional framework APIs from 
				\texttt{android.media} and \texttt{android.drm} packages and a 
				number of third-party SDKs like Vitamio and SolBox.\newline
            }
    }

\cventry
    {Feb. 2013 --\\May 2014}
    {Android developer}
    {Freelance}
    {}{}
    {Helping people from all over the world to transform their ideas into 
    production-ready Android apps.\newline}

\cventry
    {Oct. 2011 --\\Jan. 2013}
    {Android developer}
    {\href{http://mlsdev.com/}{MLSDev}}
    {Donetsk}{Ukraine}
    {Working on a number of great Android apps including aeronautical mobile 
    suite~--- a challenging GIS project with core logic built around SpatiaLite 
    extension of SQLite, carefully implemented support for both GeoJSON and 
    Shapefile geospatial vector data formats, custom map rendering based on SLD 
    styling and advanced viewer for SVG documents.\newline}

\cventry
    {Feb. 2006 --\\Jan. 2007}
    {Software developer}
    {\href{http://vuso.ua/}{VUSO}}
    {Donetsk}{Ukraine}
    {Participating in the development of IT system that was intended to 
    automate business process in an insurance company. Specifically I worked on 
    a `Clients' and `Financial' modules of the system.}


\medskip
\section{Education}

\cventry
    {2007--2010}
    {PhD in Information Technology}
    {Donetsk National Technical University}
    {}
    {\newline\textit{Not complete}}
    {My research was concerned with solving complex combinatorial problem that
    arises in the area of manufacturing resource planning. In addition to the
    theoretical research a solver for one special one-dimensional cutting stock
    problem was implemented and released as an open-source library written in
    Java. Hybrid genetic algorithm was used to discover cutting patterns with
    low trim loss and schedule production in the right order.\newline}
    
\cventry
    {2001--2006}
    {MS in Computer Science}
    {Donetsk National Technical University}
    {}
    {\newline\textit{Diploma with distinction}}
    {Experimenting with evolutionary computation algorithms in the area of the
    prediction systems.}


\medskip
\nocite{*}
\renewcommand{\bibliographyitemlabel}{[\arabic{enumiv}]}
\bibliographystyle{unsrt}
\begin{flushleft}
\bibliography{bibliography_en}
\end{flushleft}


\medskip
\section{Languages}
\cvitem{Native}{Russian, Ukrainian}
\cvitem{Intermediate}{English}


\medskip
\section{Interests}

\cvline
    {}{Computational intelligence, Formula One, football, hiking.}

\setcounter{footnote}{1}
\vfill
\enlargethispage{\footskip}
\footnotetext{\textcolor{color2}{Opening quote belongs to Chet Haase.}}

\end{document}